---
title: "Analysis"
author: "Alexis Hill"
date: "12/19/2022"
output: html_document
---

### Libraries
```{r, echo = FALSE, message = FALSE, warning=FALSE}
require(ggplot2)
require(tidyverse)
require(cowplot)
require(scales)
require(kableExtra)
```

#### Summary


Common Functions & Base directory 
```{r, echo = FALSE, message = FALSE, warning=FALSE}
# Functions & Variables I use a lot
date <- "12192022"
filedir <- paste("/stor/scratch/Wilke/amh7958/phix174-simulation/output/", date, "/", sep="")
figdir <- paste("/stor/scratch/Wilke/amh7958/phix174-simulation/src/python/main/", date, "/", "figures/", sep="")

my_palette = c("#d0a34f","#75c130", "#c12c04", "#ecd575", "#b69507",
            "#e37c71", "#adcb40", "#d3ad40", "#288ede", "#a5bdfa",
            "#93c9ff")

# get_reports() retrieves the reports for all the simulation runs in a specified scenario
# had hardcoded case for Scenario B where there is no simulation 1
get_reports <- function(filedir){
  report <- data.frame()
   batch <- 1:20

  
  for(i in batch){
     sim = read_csv(paste0(filedir, "", "sim_", i, "_report.csv")) 
     sim$sim = i
     report <- rbind(report, sim)}
  return(report)
}

get_single_report <- function(filedir, sim){
  return(read_csv(paste0(filedir, "", "sim_", sim, "_report.csv"))) 
}

best_gen <- function(filedir) {
  get_reports(filedir) %>% 
  group_by(sim) %>% 
  mutate(final_min_error = min(min_error)) %>% 
  filter(error == final_min_error) %>%  
  filter(row_number()==1) %>% 
  #filter(min_error < 2) %>% 
  arrange(min_error)
}

# plot_reports() plots the RMSE v generations for all the simulations in a given scenario
plot_reports <- function(filedir,  title){
  x_scale <- c(0, 100, 200, 300, 400, 500)
  
  figure <- get_reports(filedir) %>% 
    # filter(!is.na(gen)) %>% 
    filter(gen > 0) %>% 
    filter(error < 100) %>% 
    ggplot(aes(x = gen)) +
    geom_line(aes(y = error, color = "error"), color = "#CC79A7") + 
    geom_line(aes(y = min_error, color = "min error"), color = "black") +
    facet_wrap(~sim) + 
    #ggtitle(title) + 
    xlab("Generations") +
    ylab("RMSE") + 
    #ylim(c(1, 10)) + 
    #scale_x_continuous(breaks = x_scale) + 
    cowplot::theme_minimal_grid(12) + 
    theme(axis.text.x = element_text(size=11, angle= -45))
  
  return(figure)
}

logel_plot <- function(filedir, sim, gen, timestamp){
  
  my_palette = c("#d0a34f","#75c130", "#c12c04", "#ecd575", "#b69507",
            "#e37c71", "#adcb40", "#d3ad40", "#288ede", "#a5bdfa",
            "#93c9ff")

  figure <- read_tsv(paste0(filedir,"sim_", sim, "_gen_", gen, "_ID_0", ".tsv" )) %>% 
       mutate(time = round(time)) %>% 
       filter(time == timestamp) %>% 
       filter(!str_detect(species, '__|bound|ecoli|promoter|degraded')) %>% 
       #mutate(normalized = transcript/transcript[1]) %>% 
       mutate(species = factor(species, c("gene_A", "gene_A*", "gene_B",
                                         "gene_K", "gene_C", "gene_D",
                                         "gene_E", "gene_J", "gene_F",
                                         "gene_G", "gene_H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
       ggplot(aes(x=species, y=transcript, fill = species)) +
       geom_bar(stat="identity", color = "black") + 
       scale_fill_manual(values = my_palette) + 
       #scale_y_continuous() + 
       #scale_y_continuous(limits = c(0, 18),
        #                  breaks = c(0,3,6,9,12,15,18)) +
       scale_y_continuous(limits = c(0, 300), expand = c(0,0)) +
       ylab("")+
       cowplot::theme_cowplot(12) +
       theme(legend.position = "none") 
  
  return(figure)
}

logel_plot_2 <- function(df){
  
  my_palette = c("#d0a34f","#75c130", "#c12c04", "#ecd575", "#b69507",
            "#e37c71", "#adcb40", "#d3ad40", "#288ede", "#a5bdfa",
            "#93c9ff")

  figure <- df %>% 
       filter(!str_detect(species, '__|bound|ecoli|promoter|degraded')) %>% 
       #mutate(normalized = transcript/transcript[1]) %>% 
       mutate(species = factor(species, c("gene_A", "gene_A*", "gene_B",
                                         "gene_K", "gene_C", "gene_D",
                                         "gene_E", "gene_J", "gene_F",
                                         "gene_G", "gene_H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
       ggplot(aes(x=species, y=transcript, fill = species)) +
       geom_bar(stat="identity", color = "black") + 
       scale_fill_manual(values = my_palette) + 
       #scale_y_continuous() + 
       #scale_y_continuous(limits = c(0, 18),
        #                  breaks = c(0,3,6,9,12,15,18)) +
       scale_y_continuous(limits = c(0, 300), expand = c(0,0)) +
       ylab("") +
       xlab("genes") + 
       cowplot::theme_cowplot(12) +
       theme(legend.position = "none") 
  
  return(figure)
}

get_fitness <- function(file, timepoint){
  
  pt_run <- as.data.frame(read_tsv(file)) %>% 
    mutate(time = round(time, 0)) %>% 
    filter(time == timepoint) %>% 
    filter(!str_detect(species, '__|bound|ecoli|promoter')) %>% 
    mutate(species = factor(species, c("gene_A", "gene_A*", "gene_B",
                                           "gene_K", "gene_C", "gene_D",
                                           "gene_E", "gene_J", "gene_F",
                                           "gene_G", "gene_H"),
                                     c("A", "A*", "B", "K",
                                           "C", "D", "E", "J",
                                           "F", "G", "H"))) %>% 
    filter(species %in% c("B", "D", "J", "F", "G", "H")) %>% 
    select(-ribo_density, -transcript, -time) %>% 
    mutate(copies = c(60, 240, 60, 60, 12, 60))  %>% # From Leuven 2020
    mutate(stoich = protein/copies) %>%
    summarise(virions = min(stoich))
  
  return(pt_run$virions[1])
}

logel_timeseries_with_pcr <- function(filedir, sim, gen1, gen2, gen3, timestamp) {
  
 
  my_palette = c("#d0a34f","#75c130", "#c12c04", "#ecd575", "#b69507",
            "#e37c71", "#adcb40", "#d3ad40", "#288ede", "#a5bdfa",
            "#93c9ff")
  
  sim_qpcr <- data.frame(species = c("A", "A*", "B", "K","C", "D", "E", "J","F", "G", "H"),
                        normalized = c(17, 17, 102, 102, 102, 289, 289, 289, 187, 85, 17)) %>% 
            mutate(species = factor(species, c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
            ggplot(aes(x=species, y=normalized, fill = species)) +
            geom_bar(stat="identity", color = "black") + 
            scale_fill_manual(values = my_palette) + 
            scale_y_continuous(limits = c(0, 300)) + 
            #breaks = c(0,3,6,9,12,15,18)) + 
            ggtitle("Target (qPCR)") + 
            ylab("Relative transcripts")+ 
            xlab("ΦX174 genes")+ 
            cowplot::theme_cowplot(12) +
            theme(legend.position = "none",
                  plot.title = element_text(hjust = 0.5)) 
  
  sim_start <- logel_plot(filedir, sim, gen = gen1, timestamp = timestamp) + 
               ggtitle(paste0("Generation ", gen1)) + 
               theme(plot.title = element_text(hjust = 0.5))
  sim_middle <- logel_plot(filedir, sim, gen = gen2, timestamp = timestamp) + 
                ggtitle(paste0("Generation ", gen2)) +
                theme(plot.title = element_text(hjust = 0.5))
  sim_end <- logel_plot(filedir, sim, gen = gen3, timestamp = timestamp) + 
               ggtitle(paste0("Final", "")) + 
               theme(plot.title = element_text(hjust = 0.5))
  
  #title <- ggdraw() + draw_label(paste0("", "Simulated Transcription Patterns"))
  
  figure <- cowplot::plot_grid(sim_qpcr, sim_start, sim_middle, sim_end,
                      #label_x = "genes", label_y = "transcript abundances", 
                      #labels = c("A", "B", "", ""), 
                      ncol = 4, nrow = 1)
  
  #figure <- plot_grid(panels, ncol=1, rel_heights=c(0.1, 1)) 
               
  return(figure)
}

logel_timeseries_with_rnaseq <- function(filedir, sim, gen1, gen2, gen3, timestamp) {
  
 
  my_palette = c("#d0a34f","#75c130", "#c12c04", "#ecd575", "#b69507",
            "#e37c71", "#adcb40", "#d3ad40", "#288ede", "#a5bdfa",
            "#93c9ff")
  
  sim_qpcr <- data.frame(species = c("A", "A*", "B", "K","C", "D", "E", "J","F", "G", "H"),
                        normalized = c(27, 27, 120, 81, 123, 228, 201, 264, 231, 118, 76)) %>% 
            mutate(species = factor(species, c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
            ggplot(aes(x=species, y=normalized, fill = species)) +
            geom_bar(stat="identity", color = "black") + 
            scale_fill_manual(values = my_palette) + 
            scale_y_continuous(limits = c(0, 300), expand = c(0,0)) + 
            #breaks = c(0,3,6,9,12,15,18)) + 
            ggtitle("Target (RNAseq)") + 
            ylab("Transcripts")+ 
            xlab("ΦX174 genes")+ 
            cowplot::theme_cowplot(12) +
            theme(legend.position = "none",
                  plot.title = element_text(hjust = 0.5)) 
  
  sim_start <- logel_plot(filedir, sim, gen = gen1, timestamp = timestamp) + 
               ggtitle(paste0("Generation ", gen1)) + 
               theme(plot.title = element_text(hjust = 0.5))
  sim_middle <- logel_plot(filedir, sim, gen = gen2, timestamp = timestamp) + 
                ggtitle(paste0("Generation ", gen2)) +
                theme(plot.title = element_text(hjust = 0.5))
  sim_end <- logel_plot(filedir, sim, gen = gen3, timestamp = timestamp) + 
               ggtitle(paste0("Final", "")) + 
               theme(plot.title = element_text(hjust = 0.5))
  
  #title <- ggdraw() + draw_label(paste0("", "Simulated Transcription Patterns"))
  
  figure <- cowplot::plot_grid(sim_qpcr, sim_start, sim_middle, sim_end,
                      #label_x = "genes", label_y = "transcript abundances", 
                      #labels = c("A", "B", "", ""), 
                      ncol = 4, nrow = 1)
  
  #figure <- plot_grid(panels, ncol=1, rel_heights=c(0.1, 1)) 
               
  return(figure)
}

exp_rnaseq <- function() {
  figure <- data.frame(species = c("A", "A*", "B", "K","C", "D", "E", "J","F", "G", "H"),
                        normalized = c(27, 27, 120, 81, 123, 228, 201, 264, 231, 118, 76)) %>% 
            mutate(species = factor(species, c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
            ggplot(aes(x=species, y=normalized, fill = species)) +
            geom_bar(stat="identity", color = "black") + 
            scale_fill_manual(values = my_palette) + 
            scale_y_continuous(limits = c(0, 300)) + 
            #breaks = c(0,3,6,9,12,15,18)) + 
            ggtitle("Target (RNA-seq)") + 
            ylab("Transcripts")+ 
            xlab("genes")+ 
            cowplot::theme_cowplot(12) +
            theme(legend.position = "none",
                  plot.title = element_text(hjust = 0.5)) 
  return(figure)
}

exp_qpcr <- function() {
  figure <- data.frame(species = c("A", "A*", "B", "K","C", "D", "E", "J","F", "G", "H"),
                        normalized = c(17, 17, 102, 102, 102, 289, 289, 289, 187, 85, 17)) %>% 
            mutate(species = factor(species, c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
            ggplot(aes(x=species, y=normalized, fill = species)) +
            geom_bar(stat="identity", color = "black") + 
            scale_fill_manual(values = my_palette) + 
            scale_y_continuous(limits = c(0, 300)) + 
            #breaks = c(0,3,6,9,12,15,18)) + 
            ggtitle("Target (qPCR)") + 
            ylab("Transcripts")+ 
            xlab("genes")+ 
            cowplot::theme_cowplot(12) +
            theme(legend.position = "none",
                  plot.title = element_text(hjust = 0.5)) 
  return(figure)
}

transcripts_vs_time_plot <- function(filedir, sim, gen){
  
  my_palette = c("#d0a34f","#75c130", "#c12c04", "#ecd575", "#b69507",
            "#e37c71", "#adcb40", "#d3ad40", "#288ede", "#a5bdfa",
            "#93c9ff")

  figure <- read_tsv(paste0(filedir,"sim_", sim, "_gen_", gen, "_ID_0", ".tsv" )) %>% 
       filter(!str_detect(species, '__|bound|ecoli|promoter|degraded')) %>% 
       mutate(species = factor(species, c("gene_A", "gene_A*", "gene_B",
                                         "gene_K", "gene_C", "gene_D",
                                         "gene_E", "gene_J", "gene_F",
                                         "gene_G", "gene_H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
       ggplot(aes(x=time, y=transcript, color = species)) +
       geom_line() + 
       scale_color_manual(values = my_palette) + 
       ylab("Transcript counts")+
       cowplot::theme_cowplot(12)
  
  return(figure)
}

```

Manual test of phiX174 simulation w/ cryptic promoter btss49 & cryptic terminator RUT3, in original positions. Btss49 overlaps with the RBS for gene C. This doesn't break the simulation but results in truncated gene C products that aren't recorded by pinetree, so the gene C transcript output is lower than expected. 

```{r}
filedir <- paste("/stor/scratch/Wilke/amh7958/phix174-simulation/src/python/main/", date, "/", "test_pred_elements/", sep="")

sim_data <- data.frame()
for(i in 1:5){
     tmp <- read_tsv(paste0(filedir, "sim_test_pred_gen_", i, ".tsv")) %>%
       mutate(time = round(time)) %>% 
       filter(time == 500)
     sim_data <- rbind(sim_data, tmp)}

sim_data <- sim_data %>% 
  group_by(species) %>%
  summarise(protein=mean(protein), transcript=mean(transcript), ribo_density=mean(ribo_density))


logel_plot_2(sim_data) + ggtitle("Simulation")
```

Second manual test with cryptic promoter moved back 48 nt so that it no longer overlaps with gene C RBS.

```{r}
filedir <- paste("/stor/scratch/Wilke/amh7958/phix174-simulation/src/python/main/", date, "/", "test_pred_elements/", sep="")

sim_data <- data.frame()
for(i in 6:10){
     tmp <- read_tsv(paste0(filedir, "sim_test_pred_gen_", i, ".tsv")) %>%
       mutate(time = round(time)) %>% 
       filter(time == 500)
     sim_data <- rbind(sim_data, tmp)}

sim_data <- sim_data %>% 
  group_by(species) %>%
  summarise(protein=mean(protein), transcript=mean(transcript), ribo_density=mean(ribo_density))


logel_plot_2(sim_data) + ggtitle("Simulation")
```

```{r}
filedir <- paste("/stor/scratch/Wilke/amh7958/phix174-simulation/output/", date, "/", sep="")
sim_data <- data.frame()
for(i in 0:4){
     tmp <- read_tsv(paste0(filedir, "sim_7_gen_2878_ID_", i, ".tsv")) %>%
       mutate(time = round(time)) %>% 
       filter(time == 500)
     sim_data <- rbind(sim_data, tmp)}

filedir <- paste("/stor/scratch/Wilke/amh7958/phix174-simulation/output/", "11162022/", sep="")

sim_data_2 <- data.frame()
for(i in 0:4){
     tmp <- read_tsv(paste0(filedir, "sim_18_gen_3310_ID_", i, ".tsv")) %>%
       mutate(time = round(time)) %>% 
       filter(time == 500)
     sim_data_2 <- rbind(sim_data_2, tmp)}

sim_data <- sim_data %>% 
  group_by(species) %>%
  summarise(protein=mean(protein), transcript=mean(transcript), ribo_density=mean(ribo_density))

sim_data_2 <- sim_data_2 %>% 
  group_by(species) %>%
  summarise(protein=mean(protein), transcript=mean(transcript), ribo_density=mean(ribo_density))

rnaseq_plot <- exp_rnaseq()
qpcr_plot <- exp_qpcr()
sim_plot <- logel_plot_2(sim_data) + ggtitle("Fitted simulation (RNA-seq)")
sim_plot_2 <- logel_plot_2(sim_data_2) + ggtitle("Fitted simulation (qPCR)")

cowplot::plot_grid(rnaseq_plot, sim_plot, qpcr_plot, sim_plot_2,
                      #label_x = "genes", label_y = "transcript abundances", 
                      #labels = c("A", "B", "", ""), 
                      ncol = 2, nrow = 2)
ggsave("figures/rnaseq_qpcr_comp_barplot.png", width = 5, height = 5)
```

```{r}
plot_reports(filedir, "RNAseq")
ggsave("figures/fit_to_rnaseq_rmse.png", width = 9, height = 5)
```
```{r}
best_gen_report <- best_gen(filedir)
best_gen_report
```

```{r}
logel_timeseries_with_rnaseq(filedir, "7", "0", "500", "3878", 500)
ggsave("figures/fit_to_rnaseq_timeseries.png", width = 9, height = 5)
```

```{r}
# pA/tH correlation with worst 6 fits removed
pa_ph_corr <- best_gen_report %>% mutate(tH_mut = 1 - tH) %>%
        filter(final_min_error <= 24) %>%
        ggplot(aes(x=pA, y=tH)) +
         geom_point() + 
         scale_x_continuous(trans = "log10") +
         scale_y_continuous(trans = "log10") +
         geom_smooth(method = lm) +
         ylab("tH") +
         cowplot::theme_cowplot(12) 
pa_ph_corr
```

```{r}
# Fitted parameter distributions - boxplots
promoter_dist <- best_gen_report %>% 
  filter(final_min_error <= 24) %>%
  select(-1:-2, -12:-15) %>%
  pivot_longer(!sim, names_to = "element", values_to = "strength") %>%
  filter(element %in% c("pA", "pB", "pD", "btss49")) %>%
  ggplot(aes(x=element, y=strength, fill=element)) +
    geom_boxplot() +
    scale_y_continuous(limits = c(0, 40)) +
    ylab(expression("strength" ~ 
                         (10^{6} ~ M^{-1} ~ s^{-1})
                       )) +
    theme(legend.position = "none")

terminator_dist <- best_gen_report %>% 
  filter(final_min_error <= 24) %>%
  select(-1:-2, -12:-15) %>%
  pivot_longer(!sim, names_to = "element", values_to = "strength") %>%
  filter(element %in% c("RUT3", "tF", "tG", "tJ", "tH")) %>%
  ggplot(aes(x=element, y=strength, fill=element)) +
    geom_boxplot() +
    scale_y_continuous(limits = c(0, 1)) +
    ylab("termination probability") +
    theme(legend.position = "none")

cowplot::plot_grid(promoter_dist, terminator_dist, pa_ph_corr,
                      #label_x = "genes", label_y = "transcript abundances", 
                      #labels = c("A", "B", "", ""), 
                      ncol = 3, nrow = 1)
ggsave("figures/fit_to_rnaseq_parameter_plots.png", width = 9, height = 5)
```

