---
title: "2252022_analysis"
author: "Tanvi Ingle"
date: "3/1/2022"
output: html_document
---

Libraries 
```{r, echo = FALSE, message = FALSE, warning=FALSE}
require(ggplot2)
require(tidyverse)
require(cowplot)
require(scales)
require(kableExtra)
```

Common Functions & Base directory 
```{r, echo = FALSE, message = FALSE, warning=FALSE}
# Functions & Variables I use a lot
basedir <- "/stor/work/Wilke/tingle/phix174/output/2252022/"

# get_reports() retrieves the reports for all the simulation runs in a specified scenario
# had hardcoded case for Scenario B where there is no simulation 1
get_reports <- function(basedir, filedir, total_sims){
  report <- data.frame()
  #if(filedir == "scenario_B/") {
  #  i = 2
  #}
  #else 
  i = 1
  while (i<=total_sims) {
    sim = read_csv(paste0(basedir, filedir, "sim_", i, "_report.csv")) 
    sim$sim = i
    report <- rbind(report, sim)
    i <- i + 1
  }
  report <- report %>% 
    select(-X1)
  return(report)
}

# plot_reports() plots the RMSE v generations for all the simulations in a given scenario
plot_reports <- function(basedir, filedir, total_sims, title){
  x_scale <- c(0, 100, 200, 300, 400, 500)
  
  figure <- get_reports(basedir, filedir, total_sims) %>% 
    filter(!is.na(gen)) %>% 
    filter(gen > 0) %>% 
    filter(error < 11) %>% 
    ggplot(aes(x = gen)) +
    geom_line(aes(y = error, color = "error"), color = "pink") + 
    geom_line(aes(y = min_error, color = "min error"), color = "black") +
    facet_wrap(~sim) + 
    ggtitle(title) + 
    xlab("Generations") +
    ylab("RMSE") + 
    ylim(c(1, 10)) + 
    scale_x_continuous(breaks = x_scale) + 
    cowplot::theme_minimal_grid(12) + 
    theme(axis.text.x = element_text(size=11, angle= -45))
  
  return(figure)
}

# logel_plot() recreates the barplot transcript abundances from Logel 2020
# sim = simulation number, gen = generation of interest within the simulation, timestamp = pinetree run
logel_plot <- function(basedir, filedir, sim, gen, timestamp){
  
  my_palette = c("#d0a34f","#75c130", "#c12c04", "#ecd575", "#b69507",
            "#e37c71", "#adcb40", "#d3ad40", "#288ede", "#a5bdfa",
            "#93c9ff")

  figure <- read_tsv(paste0(basedir, filedir,"sim_", sim, "_gen_", gen, ".tsv" )) %>% 
       mutate(time = round(time)) %>% 
       filter(time == timestamp) %>% 
       filter(!str_detect(species, '__|bound|ecoli|promoter')) %>% 
       mutate(normalized = transcript/transcript[1]) %>% 
       mutate(species = factor(species, c("gene_A", "gene_A*", "gene_B",
                                         "gene_K", "gene_C", "gene_D",
                                         "gene_E", "gene_J", "gene_F",
                                         "gene_G", "gene_H"),
                                       c("A", "A*", "B", "K",
                                         "C", "D", "E", "J",
                                         "F", "G", "H"))) %>% 
       ggplot(aes(x=species, y=normalized, fill = species)) +
       geom_bar(stat="identity", color = "black") + 
       scale_fill_manual(values = my_palette) + 
       scale_y_continuous(limits = c(0, 18), 
                          breaks = c(0,3,6,9,12,15,18)) + 
       ylab("")+ 
       cowplot::theme_cowplot(12) +
       theme(legend.position = "none") 
  
  return(figure)
}

# logeL_timeseries called logel_plot() to show how distribution changes over time (start, middle, end)
# sim = simulation number, gen = last generation of interest, timestamp = pinetree run

logel_timeseries <- function(basedir, filedir, sim, gen, timestamp) {
  
  sim_start <- logel_plot(basedir, filedir, sim, gen = 1, timestamp = 1200)+
    ylab(paste0("Sim ", sim))
  sim_middle <- logel_plot(basedir, filedir, sim, gen = gen/2, timestamp = 1200)
  sim_end <- logel_plot(basedir, filedir, sim, gen = gen, timestamp = 1200)
  
  figure <- plot_grid(sim_start, sim_middle, sim_end, 
                      label_x = "genes", label_y = "transcript abundances", 
                      ncol = 3, nrow = 1)
                     
  return(figure)
}
```

### **Objective**
Here I will analyze the results from the promoter optimization run on 2-25-2022. These results are form the new optimization algorithm that differs from previous algorithms in several distinct ways: 

### **Change in Error over Generations**

```{r, echo = FALSE, message = FALSE, warning=FALSE}
filedir <- ""
plot_reports(basedir, filedir, 20, "qPCR Simulations")
```

### **Final Minimum Errors**

```{r, echo = FALSE, message = FALSE, warning=FALSE}
col_order = c("sim", "gen", "pA", "pB", "pD", "error", "min_error")

all_sims_report <- get_reports(basedir, filedir, 20) %>% 
  filter(!is.na(gen)) %>% 
  filter(gen == 500) %>% 
  group_by(sim)

all_sims_report <- all_sims_report[ , col_order]

kable(all_sims_report) %>% 
  kable_styling(latex_options = "striped") %>% 
  column_spec(c(1,7), bold = T)
   
```

### **Final Transcript Abundances**

```{r, echo = FALSE, message = FALSE, warning=FALSE}
logel_report <- get_reports(basedir, filedir, 20) %>% 
  group_by(sim) %>% 
  mutate(final_min_error = min(min_error)) %>% 
  filter(error == final_min_error) %>%  
  filter(row_number()==1) %>% 
  select(-error, -min_error)

logel_report <- logel_report[ , c("sim", "gen", "pA", "pB", "pD", "final_min_error")]

kable(logel_report) %>% 
  kable_styling(latex_options = "striped")

n = 1
while(n < nrow(logel_report)){
  figure <- logel_plot(basedir, filedir, 
             as.numeric(logel_report$sim[n]), as.numeric(logel_report$gen[n]), 1200) + 
    ggtitle(paste0("sim ", logel_report$sim[n], ", gen = ",logel_report$gen[n]))
  
  figure 
  n = n + 1
}

logel_plot(basedir, filedir, 12, 296, 1200)



```

> Scenario A - Evolution of transcript abundances over generations for the best sims

```{r, echo = FALSE, message = FALSE, warning=FALSE}
sim5_time <- logel_timeseries(basedir, filedir, 5, 300, 1200) 
sim6_time <- logel_timeseries(basedir, filedir, 6, 300, 1200) 
sim8_time <- logel_timeseries(basedir, filedir, 8, 300, 1200) 
#sim10_time <- logel_timeseries(basedir, filedir, 10, 300, 1200)

plot_grid(sim5_time, sim6_time, sim8_time, nrow = 3)
```

> Scenario A - Here is how the promoter values change over time 

```{r, echo = FALSE, message = FALSE, warning=FALSE}
get_reports(basedir, filedir, 10) %>% 
  filter(!is.na(gen)) %>% 
  filter(sim %in% c(5,6,8)) %>% 
  #filter(gen <= 201) %>% 
  ggplot(aes(x = gen)) +
  facet_wrap(. ~ sim) +
  geom_line(aes(y = pA)) + 
  scale_y_continuous(trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) +
  cowplot::theme_minimal_grid(12)

get_reports(basedir, filedir, 10) %>% 
  filter(!is.na(gen)) %>% 
  filter(sim %in% c(5,6,8)) %>%
  ggplot(aes(x = gen)) +
  facet_wrap(. ~ sim) +
  scale_y_continuous(trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) +
  geom_line(aes(y = pB)) + 
  cowplot::theme_minimal_grid(12)


get_reports(basedir, filedir, 10) %>% 
  filter(!is.na(gen)) %>% 
  filter(sim %in% c(5,6,8)) %>%
  ggplot(aes(x = gen)) +
  facet_wrap(. ~ sim, scales="free_y") +
  geom_line(aes(y = pD)) + 
  scale_y_continuous(trans = log10_trans(),
    breaks = trans_breaks("log10", function(x) 10^x),
    labels = trans_format("log10", math_format(10^.x))) +
  cowplot::theme_minimal_grid(12)
  
  # geom_line(aes(y = pB)) + 
  # geom_line(aes(y = pD))
```

